---
title: "fmpr"
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


The goal of fmpr is to provide a lightweight R interface to the Financial Modeling Prep API

##### Installation

You can install the development version from [GitHub](https://github.com/) with:

```{r, eval=FALSE}
#### install.packages("devtools")
devtools::install_github("zac-garland/fmpr")
```


```{r, eval=FALSE}
library(fmpr)
```


#### set api key

```{r, eval=FALSE}
fmp_api_key("demo")
```

#### Balance Sheet


```{r, eval=FALSE}
fmp_balance_sheet(ticker = "AAPL", period = "quarter")  
```

#### Cash Flow Statement


```{r, eval=FALSE}
fmp_cash_flow_statement(ticker = "AAPL", period = "quarter")  
```


#### Company Profile

```{r, eval=FALSE}
fmp_company_profile(ticker = "AAPL")  
```

#### Discounted Cash Flow

```{r, eval=FALSE}
fmp_historical_discounted_cash_flow(ticker = "AAPL")  
```



#### Enterprise Value
```{r, eval=FALSE}
fmp_enterprise_value(ticker = "AAPL", period = "quarter")  
```


#### Financial Growth
```{r, eval=FALSE}
fmp_financial_growth(ticker = "AAPL", period = "quarter")  
```

#### Historical Discounted Cash Flow

```{r, eval=FALSE}
fmp_historical_discounted_cash_flow(ticker = "AAPL", period = "quarter")  
```

#### Historical Earning Calendar

```{r, eval=FALSE}
fmp_historical_earning_calendar(ticker = "AAPL")  
```

#### Historical Price

```{r, eval=FALSE}
fmp_historical_price(ticker = "AAPL",start_date = as.Date("2019-01-01"))  
```

#### Income Statement

```{r, eval=FALSE}
fmp_income_statement(ticker = "AAPL", period = "quarter")  
```

#### Intraday

```{r, eval=FALSE}
fmp_intraday(ticker = "AAPL", freq = "1min")  
```

#### Key Metrics

```{r, eval=FALSE}
fmp_key_metrics(ticker = "AAPL", period = "quarter")  
```

#### Quote

```{r, eval=FALSE}
fmp_quote(ticker = "AAPL")  
```


#### Rating

```{r, eval=FALSE}
fmp_rating(ticker = "AAPL")  
```

#### Ratios

```{r, eval=FALSE}
fmp_ratios(ticker = "AAPL", period = "quarter")  
```

#### Stock Dividend

```{r, eval=FALSE}
fmp_stock_dividend(ticker = "AAPL")  
```

#### Stock Split

```{r, eval=FALSE}
fmp_stock_split(ticker = "AAPL")  
```







